---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Lindley Slipetz"
date: "04/02/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE, warning = FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

```{r load_data}
evals <- evals
```

### Exercise 2

```{r linear_reg_1}
m_bty <- linear_reg() %>% 
            set_engine('lm') %>% 
            set_mode('regression')
m_bty_fit <- m_bty %>% 
          fit(score ~ bty_avg, data = evals)
m_bty_fit
glance(m_bty_fit$fit)
```
The model is score = 3.88034 + 0.6664bty_avg. R^2 = 0.035 and adjusted R^2 = 0.033

### Exercise 3

```{r linear_reg_2}
m_bty_gen <- linear_reg() %>% 
            set_engine('lm') %>% 
            set_mode('regression')
m_bty_gen_fit <- m_bty_gen %>% 
          fit(score ~ bty_avg + gender, data = evals)
m_bty_gen_fit
glance(m_bty_gen_fit$fit)
```



score = 3.74734 + 0.7416bty_avg + 0.17239gender. R^2 = 0.059 and adjusted R^2 = 0.055.

### Exercise 3

For someone with a 0 beauty score who is female, the average score is 3.74734. A one unit increase in score is associated with a 0.7416 point increase in beauty score, holding gender constant. A one unit increase in score is more associated with males, holding beauty score constant.

### Exercise 4

5.9% of variability in score is explained by the model.

### Exercise 5
 
The equation for just males is score = 3.91973 + 0.7416bty_avg

### Exercise 6
  
Males tend to have higher scores given the same beauty rating.

### Exercise 7

Males scores change by +0.17239, female scores change by -0.17239.


### Exercise 8 
Adjusted R^2 takes into account the number of predictors. Adjusted R^2 for m_bty was 0.033. Adjusted R^2 for m_bty_gen was R^2 = 0.055. This tells us that the addition of the gender variable increases variability explained. So, it's useful.

### Exercise 9
The slope of bty_avg was 0.6664 for m_bty. The slope of bty_avg was 0.7416. Yes, the addition of gender in the model has changed the parameter estimate for beauty. Beauty now has a greater influence when we control for gender. 


